---
title: "01-Prediction"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))
```


# Your Turn 1

Write a pipe that creates a model that uses `lm()` to fit a linear regression. Save it as `lm_spec` and look at the object. What does it return?

*Hint: you'll need https://www.tidymodels.org/find/parsnip/*

```{r}

```


# Your Turn 2

Double check. Does

```{r}
lm_fit <- fit(lm_spec,
              Sale_Price ~ Gr_Liv_Area,
              data = ames)
lm_fit
```

give the same results as

```{r}
lm(Sale_Price ~ Gr_Liv_Area, data = ames)
```


# Your Turn 3

Fill in the blanks. Use `predict()` to

1. Use your linear model to predict sale prices; save the tibble as `price_pred`.
2. Add a pipe and use `mutate()` to add a column with the observed sale prices; name it `truth`.

```{r}
lm_fit <- fit(lm_spec, Sale_Price ~ Gr_Liv_Area, data = ames)

price_pred <- ________ %>% 
  predict(new_data = ________) %>% 
  ________

price_pred
```


# Your Turn 4

Discuss in the chat which model:

1. Has the smallest residuals  
2. Will have lower prediction error. Why?  


# Your Turn 5

Use `initial_split()`, `training()`, `testing()`, `lm()` and `rmse()` to:

1. Split **ames** into training and test sets. Save the rsplit!

2. Extract the training data. Fit a linear model to it. Save the model!

3. Measure the RMSE of your linear model with your test set.  

```{r}
set.seed(100) # Important!

ames_split  <- ________
ames_train  <- ________
ames_test   <- ________

lm_fit <- fit(lm_spec,
              Sale_Price ~ Gr_Liv_Area, 
              data = ________)

price_pred <- ________ %>% 
  predict(new_data = ________) %>% 
  mutate(price_truth = ________)

lm_rmse <- rmse(________, truth = ________, estimate = ________)

lm_rmse
```


# Your Turn 6

Write a pipe to create a model that uses the {rpart} package to fit a regression tree and calculate the RMSE.

Compare to the `lm()` model. Which is better?

*Hint: you'll need https://www.tidymodels.org/find/parsnip/*

```{r}
rt_spec <- 
  ________ %>%
  set_engine(________) %>%
  set_mode(________)

dt_fit <- fit(________,
              Sale_Price ~ Gr_Liv_Area, 
              data = ________)

price_pred <- ________ %>% 
  predict(new_data = ________) %>% 
  mutate(price_truth = ________)

dt_rmse <- rmse(price_pred,
                truth = ________,
                estimate = ________)

lm_rmse

dt_rmse
```


# Your Turn 7

Write a pipe to create a model that uses the {kknn} package to fit a K nearest neighbors model. Calculate the RMSE to compare to our other models that use the same formula.

*Hint: you'll need https://www.tidymodels.org/find/parsnip/*

```{r}
knn_spec <-
  ________ %>%
  set_engine(________) %>%
  set_mode(________)

knn_fit <- fit(________,
               Sale_Price ~ Gr_Liv_Area, 
               data = ________)

price_pred  <- ________ %>% 
  predict(new_data = ________) %>% 
  mutate(price_truth = ________)

knn_rmse <- rmse(price_pred,
                 truth = ________,
                 estimate = ________)

lm_rmse

dt_rmse

knn_rmse
```
