---
title: "Data Transformation - Solutions"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

<!-- This file by Jake Thompson is licensed under a Creative Commons Attribution 4.0 International License, adapted from the orignal work at https://github.com/rstudio/master-the-tidyverse by RStudio. -->

```{r setup, include = FALSE}
library(tidyverse)
library(babynames)
library(nycflights13)
library(skimr)
```


## Your Turn 1

* Run this code to view a summary of the data

```{r}
babynames
skim(babynames)
```


## Your Turn 2

Alter the code to select just the `n` column:

```{r}
select(babynames, n)
```


## `select()` helpers

```{r}
select(storms, name:pressure)
select(storms, -c(name, pressure))
select(storms, starts_with("w"))
select(storms, ends_with("e"))
select(storms, contains("d"))
select(storms, matches("^.{4}$"))
select(storms, one_of(c("name", "names", "Name")))
```


## Consider

Which of these is NOT a way to select the `name` and `n` columns together?

```{r}
select(babynames, -c(year, sex, prop))
select(babynames, name:n)
select(babynames, starts_with("n"))
select(babynames, ends_with("n"))
```


## Your Turn 3

Show:

* All of the names where prop is greater than or equal to 0.08  
* All of the children named "Daenerys"  
* All of the names that have a missing value for `n`  

```{r}
filter(babynames, prop >= 0.08)
filter(babynames, name == "Daenerys")
filter(babynames, is.na(n))
```


## Your Turn 4

Use Boolean operators to alter the code below to return only the rows that contain:

* Girls named Sea  
* Names that were used by exactly 5 or 6 children in 1880  
* Names that are one of Acura, Lexus, or Yugo

```{r}
filter(babynames, name == "Sea", sex == "F")
filter(babynames, n == 5 | n == 6, year == 1880)
filter(babynames, name %in% c("Acura", "Lexus", "Yugo"))
```


## Your Turn 5

Arrange babynames by `n`. Add `prop` as a second (tie breaking) variable to arrange on. Can you tell what the smallest value of `n` is?

```{r}
arrange(babynames, n, prop)
```


## Your Turn 6

* Use `desc()` to find the names with the highest prop.
* Then, use `desc()` to find the names with the highest n.

```{r}
arrange(babynames, desc(prop))
arrange(babynames, desc(n))
```


## Consider

How would you do the following to the `babynames` data:

1. Filter to only the names Sansas and Arya;
2. Arrange by `name` and then `year`; and
3. Remove the `prop` variable

One less than ideal option: nesting.

```{r}
babynames
filter(babynames, name %in% c("Sansa", "Arya"))
arrange(filter(babynames, name %in% c("Sansa", "Arya")), name, year)
select(arrange(filter(babynames, name %in% c("Sansa", "Arya")), name, year), -prop)
```

Another less than ideal option: intermediate objects.

```{r}
bn1 <- babynames
bn2 <- filter(bn1, name %in% c("Sansa", "Arya"))
bn3 <- arrange(bn2, name, year)
bn4 <- select(bn3, -prop)
```


## Reconsider

How would you do the following to the `babynames` data:

1. Filter to only the names Sansas and Arya;
2. Arrange by `name` and then `year`; and
3. Remove the `prop` variable

A better way: pipes.

```{r}
babynames %>%
  filter(name %in% c("Sansa", "Arya")) %>%
  arrange(name, year) %>%
  select(-prop)
```


## Your Turn 7

Use `%>%` to write a sequence of functions that: 

1. Filter babynames to just the girls that were born in 2015  
2. Select the `name` and `n` columns  
3. Arrange the results so that the most popular names are near the top.

```{r}
babynames %>% 
  filter(year == 2015, sex == "F") %>% 
  select(name, n) %>% 
  arrange(desc(n))
```


## Your Turn 8

1. Trim `babynames` to just the rows that contain your `name` and your `sex`  
2. Trim the result to just the columns that will appear in your graph (not strictly necessary, but useful practice)  
3. Plot the results as a line graph with `year` on the x axis and `prop` on the y axis, colored by `sex`

```{r}
babynames %>% 
  filter(name == "Jake") %>% 
  select(year, prop, sex) %>% 
  ggplot(mapping = aes(x = year, y = prop)) +
    geom_line(mapping = aes(color = sex))
```


## Your Turn 9

Use `summarize()` to compute three statistics about the data:

1. The first (minimum) year in the data set  
2. The last (maximum) year in the data set  
3. The total number of unique names in the data set

```{r}
babynames %>% 
  summarize(first = min(year), 
            last = max(year), 
            num_names = n_distinct(name))
```


## Your Turn 10

Extract the rows where `name == "Khaleesi"`. Then use `summarize()` to find:

1. The total number of children named Khaleesi
2. The first year Khaleesi appeared in the data

```{r}
babynames %>% 
  filter(name == "Khaleesi") %>% 
  summarize(total = sum(n), first = min(year))
```


## Your Turn 11

Calculate popularity by determining the total number of children given each name.

1. Use **`group_by()`** and **`summarize()`** to calculate the total number of children that have been given each name, by sex.
2. Arrange the results to show the most popular names first.

Bonus:

3. Create a bar plot of the 10 most popular names, with **`name`** on the x-axis and total children on the y-axis.


```{r}
babynames %>%
  group_by(name, sex) %>% 
  summarize(total = sum(n)) %>% 
  arrange(desc(total))
```

```{r}
babynames %>%
  group_by(name, sex) %>% 
  summarize(total = sum(n)) %>% 
  arrange(desc(total)) %>%
  slice_max(total, n = 10) %>%
  ggplot(mapping = aes(x = fct_reorder(name, desc(total)), y = total)) +
  geom_col(mapping = aes(fill = sex)) +
  scale_fill_brewer() +
  labs(x = "Name", y = "Total Children") +
  theme_bw()
```


## Your Turn 12

* Use grouping to calculate and then plot the number of children born each year over time.
* Plot the results as a line graph.

```{r}
babynames %>%
  group_by(year) %>% 
  summarize(n_children = sum(n)) %>% 
  ggplot(mapping = aes(x = year, y = n_children)) +
  geom_line()
```


## Mutate

```{r}
babynames %>%
  mutate(percent = round(prop * 100, 2))
```


## Your Turn 13

Use `min_rank()` and `mutate()` to rank each row in `babynames` from largest `prop` to lowest `prop`.

```{r}
babynames %>% 
  mutate(rank = min_rank(desc(prop)))
```


## Your Turn 14

* Compute each name's rank _within its year and sex_. 
* Then compute the median rank _for each combination of name and sex_, and arrange the results from highest median rank to lowest.

```{r}
babynames %>% 
  group_by(year, sex) %>% 
  mutate(rank = min_rank(desc(prop))) %>% 
  group_by(name, sex) %>% 
  summarize(score = median(rank)) %>% 
  arrange(score)
```


## Flights data
```{r}
flights
skim(flights)
```


## Toy data

```{r}
heroes <- tribble(
  ~hero,           ~identity,
  "Iron Man",      "Tony Stark",
  "Spider-Man",    "Peter Parker",
  "Black Panther", "T'Challa"
)

homes <- tribble(
  ~hero,           ~home,
  "Thor",          "Asgard",
  "Spider-Man",    "Queens",
  "Black Panther", "Wakanda"
)

enemies <- tribble(
  ~avenger,        ~villain,
  "Thor",          "Loki",
  "Spider-Man",    "Mysterio",
  "Black Panther", "Killmonger"
)
```


## Mutating joins

```{r}
left_join(heroes, homes, by = "hero")

right_join(heroes, homes, by = "hero")

full_join(heroes, homes, by = "hero")

inner_join(heroes, homes, by = "hero")
```


## Your Turn 15

Which airlines had the largest arrival delays (**`arr_delay`**)? Complete the code below.

1. Join `airlines` to `flights`
2. Compute and order the average arrival delays by airline. Display full names, no codes.

```{r}
flights %>% 
  drop_na(arr_delay) %>%
  left_join(airlines, by = "carrier") %>%
  group_by(name) %>%
  summarize(delay = mean(arr_delay)) %>%
  arrange(delay)
```


## Different names

```{r}
heroes %>% left_join(enemies, by = c("hero" = "avenger"))
```


## Filtering joins

```{r}
semi_join(heroes, homes, by = "hero")

anti_join(heroes, homes, by = "hero")
```


## Your Turn 16

How many airports in `airports` are serviced by flights originating in New York (i.e. flights in our data set?) Notice that the column to join on is named `faa` in the **airports** data set and `dest` in the **flights** data set.


```{r}
airports %>%
  semi_join(flights, by = c("faa" = "dest")) %>%
  distinct(faa)
```


***

# Take aways

* Extract variables with `select()`  
* Extract cases with `filter()`  
* Arrange cases, with `arrange()`  

* Make tables of summaries with `summarize()`  
* Make new variables, with `mutate()`  
* Do groupwise operations with `group_by()`

* Connect operations with `%>%`  

* Use `left_join()`, `right_join()`, `full_join()`, or `inner_join()` to join data sets
* Use `semi_join()` or `anti_join()` to filter data sets against each other
