---
title: "Resampling - Solutions"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
```


# Your Turn 1

Use `bootstraps()` to create 100 bootstrap samples of the `penguins` data. Save the bootstrap samples as `penguin_boot`. Keep `set.seed(100)`!

```{r}
set.seed(100)
penguin_boot <- bootstraps(penguins, times = 100)
penguin_boot
```


# Your Turn 2

Complete the code to calculate the correlation for the fifth bootstrap sample.

```{r}
boot5 <- penguin_boot$splits[[5]]
boot_sample <- analysis(boot5)
cor(boot_sample$bill_length_mm, boot_sample$bill_depth_mm,
    use = "complete.obs")
```


# Your Turn 3

Use the mapping functions and `mutate()` to calculate the correlation between bill length and bill depth.

1. Write a function to calculate the correlation from the analysis set of a split.

2. Apply that function to every bootstrap sample using `mutate()` and mapping function.

3. Make a histogram of the bootstrapped correlations.

```{r}
penguin_cor <- function(split) {
  boot_sample <- analysis(split)
  cor(boot_sample$bill_length_mm, boot_sample$bill_depth_mm,
      use = "complete.obs")
}

penguin_boot %>%
  mutate(corr = map_dbl(splits, penguin_cor)) %>%
  ggplot(mapping = aes(x = corr)) +
  geom_histogram()
```


# Your Turn 4

1. Use `initial_split()` to create a training and testing set of the penguins data.

2. Write a parsnip specification to fit a linear model that uses flipper length to predict bill length.

3. Use the testing data to calculate the RMSE.

```{r}
penguin_split <- initial_split(penguins)
penguin_train <- training(penguin_split)
penguin_test <- testing(penguin_split)

lm_spec <- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")

lm_model <- fit(lm_spec,
                bill_length_mm ~ flipper_length_mm,
                data = penguin_train)

lm_preds <- predict(lm_model, new_data = penguin_test) %>%
  mutate(.truth = penguin_test$bill_length_mm)

rmse(lm_preds, truth = .truth, estimate = .pred)
```


# Your Turn 5

What would happen if you repeated this process? Would you get the same answers?

Rerun the code chunk from the last exercise. Do you get the same answer?

```{r}
penguin_split <- initial_split(penguins)
penguin_train <- training(penguin_split)
penguin_test <- testing(penguin_split)

lm_spec <- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")

lm_model <- fit(lm_spec,
                bill_length_mm ~ flipper_length_mm,
                data = penguin_train)

lm_preds <- predict(lm_model, new_data = penguin_test) %>%
  mutate(.truth = penguin_test$bill_length_mm)

rmse(lm_preds, truth = .truth, estimate = .pred)
```


# Your Turn 6

Run the code below. What does it return?

```{r}
set.seed(100)
cv_folds <- vfold_cv(penguins, v = 10, strata = species)

cv_folds
```


# Your Turn 7

Modify the code below to estimate our model on each of the folds and calculate the average RMSE for our penguin model.

```{r}
fit_resamples(lm_spec,
              bill_length_mm ~ flipper_length_mm,
              resamples = cv_folds,
              metrics = metric_set(rmse)) %>%
  collect_metrics()
```


# Your Turn 8

Use `fit_resamples()` and `cv_folds` to estimate two models to predict bill length.

1. `bill_length_mm ~ flipper_length_mm`

2. `bill_length_mm ~ species + sex`

Compare the performance of each.

```{r}
fit_resamples(lm_spec,
              bill_length_mm ~ flipper_length_mm,
              resamples = cv_folds) %>%
  collect_metrics()

fit_resamples(lm_spec,
              bill_length_mm ~ species + sex,
              resamples = cv_folds) %>%
  collect_metrics()
```
