---
title: "Recipes"
subtitle: "Tidy Data Science with the Tidyverse and Tidymodels"
session: 13
author: W. Jake Thompson
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "assets/css/my-theme.css", "assets/css/my-fonts.css"]
    seal: false 
    lib_dir: libs
    nature:
      # autoplay: 5000
      highlightStyle: solarized-light
      highlightLanguage: ["r", "css", "yaml"]
      slideNumberFormat: "" 
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    includes:
      in_header: [assets/header.html]
params:
  site_link: "https://bit.ly/tidyds-2021"
  class_link: "https://tidyds-2021.wjakethompson.com"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(collapse = TRUE,
                      fig.retina = 3,
                      fig.path = "images/recipes/plots/",
                      fig.align = "center",
                      fig.asp = 0.618,
                      comment = "#>")

xaringanExtra::use_share_again()
xaringanExtra::use_panelset()
xaringanExtra::use_extra_styles(hover_code_line = TRUE,
                                mute_unhighlighted_code = FALSE)
xaringanExtra::use_scribble(pen_color = "#009FB7")

yt_counter <- 0
library(countdown)
library(tidyverse)
library(tidymodels)
library(flair)
library(here)
library(knitr)
library(downlit)
library(vip)

library(xaringancolor)
blue <- "#009FB7"
light_blue <- "#0ADEFF"
yellow <- "#FED766"
dark_yellow <- "#A27A01"
pink <- "#CB297B"
light_pink <- "#FF8DC6"
green <- "#5FAD56"
dark_green <- "#3C6E35"
grey <- "#696773"

library(AmesHousing)
ames <- make_ames()

lm_spec <- 
  linear_reg() %>% 
  set_engine("lm") %>% 
  set_mode("regression")

set.seed(100) # Important!
ames_split  <- initial_split(ames)
ames_train  <- training(ames_split)
ames_test   <- testing(ames_split)

theme_set(wjake::theme_wjake(base_family = "Source Sans Pro",
                             base_size = 14,
                             axis_title_size = 12))
```


class: title-slide, center

<span class="fa-stack fa-4x">
  <i class="fa fa-circle fa-stack-2x" style="color: #ffffff;"></i>
  <strong class="fa-stack-1x" style="color:#009FB7;">`r rmarkdown::metadata$session`</strong>
</span> 

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author`

#### [`r params$class_link`](`r params$class_link`) &#183; [`r params$site_link`](`r params$site_link`)

.footer-license[*Tidy Data Science with the Tidyverse and Tidymodels* is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).]

<div style = "position:fixed; visibility: hidden">
  $$\require{color}\definecolor{blue}{rgb}{0, 0.623529411764706, 0.717647058823529}$$
  $$\require{color}\definecolor{light_blue}{rgb}{0.0392156862745098, 0.870588235294118, 1}$$
  $$\require{color}\definecolor{yellow}{rgb}{0.996078431372549, 0.843137254901961, 0.4}$$
  $$\require{color}\definecolor{dark_yellow}{rgb}{0.635294117647059, 0.47843137254902, 0.00392156862745098}$$
  $$\require{color}\definecolor{pink}{rgb}{0.796078431372549, 0.16078431372549, 0.482352941176471}$$
  $$\require{color}\definecolor{light_pink}{rgb}{1, 0.552941176470588, 0.776470588235294}$$
  $$\require{color}\definecolor{grey}{rgb}{0.411764705882353, 0.403921568627451, 0.450980392156863}$$
</div>
  
<script type="text/x-mathjax-config">
  MathJax.Hub.Config({
    TeX: {
      Macros: {
        blue: ["{\\color{blue}{#1}}", 1],
        light_blue: ["{\\color{light_blue}{#1}}", 1],
        yellow: ["{\\color{yellow}{#1}}", 1],
        dark_yellow: ["{\\color{dark_yellow}{#1}}", 1],
        pink: ["{\\color{pink}{#1}}", 1],
        light_pink: ["{\\color{light_pink}{#1}}", 1],
        grey: ["{\\color{grey}{#1}}", 1]
      },
      loader: {load: ['[tex]/color']},
      tex: {packages: {'[+]': ['color']}}
    }
  });
</script>

---
class: your-turn

# Your Turn 0

.big[
* Open the R Notebook **materials/exercises/13-recipes.Rmd**
* Run the setup chunk
]

```{r yt-setwd-cd, echo = FALSE}
countdown(minutes = 1, seconds = 0,
          font_size = "2em",
          color_border = yellow,
          color_background = blue,
          color_text = yellow,
          color_running_background = "#F0F0F0",
          color_running_text = blue,
          color_finished_background = yellow,
          color_finished_text = blue)
```
